Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-13 article.tex
adding abstract + intro + start of data

\begin{abstract}
  blabla
\end{abstract}

\section{Introduction}

\section{Related works}

\section{Databases}
La base de données principale que nous allons utiliser est le résultat des recherches précédentes de Delphine PAQUIRY.
En effet, l'année dernière une partie de son stage

@@

\cite{main_database}

@@

On portera surtout notre attention sur les champs suivants :
\begin{enumerate}
    \item \textsl{longitude}, \textsl{latitude} : coordonnées de chaque site;
    \item \textsl{nom\_op} : nom commercial de l'opérateur;
    \item \textsl{nom\_reg}, \textsl{nom\_dep} et \textsl{nom\_com} : nom de la région, du département et de la commune d'implantation du site;
    \item \textsl{site\_$x$g} : équipement du site en technologie $x$G ($x\in\{ 2,\dots,5\}$);
    \item \textsl{num\_site} : identifiant du site issu du SI de l'opérateur. 
\end{enumerate}

>>>>

\begin{abstract}
  The field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\%
  in 2023 in the world, and 97\% in France. Therefore, the collected datas represent a big opportunity for telecommunication
  companies to predict their customers behaviour for internal or marketing purposes. Thus, it is primordial for these companies
  to be able to determinate if a user is moving. For that, it is necessary to understand the neighbouring relationships between the 
  telephonic base stations. This article aims at comparing different method, ellaborated in order to adaptively detect these
  relationship between telephonic base stations given their geographical positions.
\end{abstract}

\section{Introduction}
    \IEEEPARstart{T}{his} article is the continuation of the work done by Delphine Paquiry in this paper \cite{art_del_paq}.
    It aims at discovering the neighbouring relationships between base stations from their geographical positions, using a 
    measure of the density of base station.

    For that, it is necessary to describe and analyse the databases that have been used during the research, then to present 
    the different appoaches that always consist of these steps : establish a first neighbouring graph, compute the base station 
    densities and filter this graph with different criteria using this information. The final step is to present the results
    of the different approches and conclude.
\section{Related works}

\section{Databases}
    Several databases have been used in order to test the different aspects of the methods. However, one of
    them is directly necessary to the method itself.

@@

    This database \cite{main_database} contains all the information needed to the application of the method. It is from
    \acrfull{arcep}, which is a french national organisation that

    The fields that are being used here are the following :

@@
